Multilevel selection in causal models: the non-ergodicity of evolutionary and probabilistic theories as the general driver of the emergence of cooperation and specialization.

### 2022-01-20 article.tex
IRREVERSIBLE TRANSITIONS

>>>>

\section{The step into irreversible transitions, reproductive division of labour}

\begin{quotation}
A major transition is said to occur when independently replicating units evolve into groups of entities that can only replicate as part of the group and that show a relative lack of within-group conflict [1–3] \cite{gonzalesForero2021-eusociality}

Eusociality is commonly defined as involving groups with reproductive division of labour, overlapping generations and cooperative work
\end{quotation}
